---
title: "Tweet Analysis"
author: "Your Name"
date: "Date"
output:
  slidy_presentation: default
  html_document: default
params:
  file: "/path/to/your/file.csv"
  words: !r c("enter", "your", "most", "important", "keywords", "here")
---

```{r setup, include=FALSE}
library(knitr)
library(readr)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(advertools)
library(DT)
library(viridis)
knitr::opts_chunk$set(echo = FALSE, fig.width = 13, 
                      fig.height = 5, fig.align = "center")

tweets_df <- read_csv(params$file)
#tweets_df <- read_csv("~/Downloads/sna_tweets_mayjunjul.csv")
#tweets_df$`Tweet text` <- iconv(tweets_df$`Tweet text`, "ASCII", "UTF-8", "byte")
tweets_df$date <- as.POSIXct(gsub(" \\+0000", "", tweets_df$time))
tweets_df$month <- month(as.Date(tweets_df$time), label = TRUE)
tweets_df$wday <- wday(as.Date(tweets_df$time), label = TRUE)
```

## Monthly & Weekday Tweets

```{r monthly_tweets}
monthly_tweets <- tweets_df %>% 
  group_by(month) %>% 
  summarise(tweets = n(), impressions = sum(impressions, na.rm = TRUE),
            engagements = sum(engagements, na.rm = TRUE), 
            eng_rate = round(engagements / impressions, digits = 3))

datatable(monthly_tweets, rownames = FALSE, options = list(dom = "t"), 
          width = "60%") %>% 
  formatCurrency(columns = 1:4, currency = "", digits = 0) %>% 
  formatPercentage(columns = 5, digits = 1)

wday_tweets <- tweets_df %>% 
  group_by(wday) %>% 
  summarise(tweets = n())

datatable(wday_tweets, rownames = F, options = list(dom = "t"), 
          width = "60%") %>% 
  formatCurrency(currency = "", digits = 0, columns = T)


```

* Tweet numbers are exact, metrics are approximated. They are the metrics of the tweets and not months.

## Daily Tweet Activity

```{r daily_tweets}

daily_tweets <- tweets_df %>% 
  group_by(date) %>% 
  summarise(tweets = n(), impressions = sum(impressions, na.rm = T),
            engagements = sum(engagements, na.rm = T),
            eng_rate = round(engagements / impressions, digits = 2))
```


```{r daily_tweet_plot}
daily_tweets_plot <- ggplot(daily_tweets, aes(as.Date(date), 
                           tweets, fill = wday(as.Date(date), label = T))) +
  geom_bar(stat = "identity") +
  scale_x_date(date_labels = "%b %d") +
  scale_fill_viridis(discrete = T, name = NULL) +
  labs(x = NULL, y = "Tweets")
daily_tweets_plot
```

## Hourly Tweet Activity

```{r hourly_tweet_plot}
hourly <- tweets_df %>% 
  group_by(hour = hour(date)) %>% 
  summarise(tweets = n())

hourly_tweet_plot <- ggplot(hourly, aes(hour, tweets)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = tweets), col = "white", vjust = 1.2) +
  scale_x_continuous(breaks = seq(0,23,1))
hourly_tweet_plot

```

## Followers From Tweets

```{r followers_from_tweets}
tweets_df %>% select(`Tweet text`, follows, `promoted follows`) %>% 
  arrange(desc(follows)) %>% 
  datatable(options = list(dom = "tpli")) %>% 
  formatCurrency(columns = 2:3, digits = 0, currency = "")
```

## Most Used Words - absolute and weighted frequency

```{r word_freq, warning=FALSE}
tweets_freq <- word_frequency(tweets_df[c(3,5)], rm_words = stopwords_en)

datatable(tweets_freq, filter = "top", extensions = "Scroller",
          colnames = c("tweet" = "text", "impressions" = "original_metric"), 
          options = list(scroller =T, scrollY = 350, scrollX = 1000, dom = "ltip")) %>% 
  formatCurrency(columns = c(2,3,7), currency = "", digits = 0) %>% 
  formatPercentage(columns = 4:5, digits = 1)
```

- **abs_freq:** the absolute number of times this word was used
- **wtd_freq:** `abs_freq` * impressions of the tweets where this word was used (weighted frequency)
- **cum_perc:** cumulative percentage of `wtd_freq`
- **perc:** percenage occurences of this word in all tweets


```{r content_analysis}
my_words <- params$words
tweets_hashtag <- twtr_get_hashtags(tweets_df$`Tweet text`)
tweets_mention <- twtr_get_mentions(tweets_df$`Tweet text`)
tweets_url <- twtr_get_urls(tweets_df$`Tweet text`)
tweets_word <- twtr_get_words(tweets_df$`Tweet text`,words = my_words)
```

## Hashtag Summary

```{r hashtag_summary, fig.height=4}
datatable(tweets_hashtag$hashtag_summary, rownames = F, 
          options = list(dom = "t"), width = "60%") %>% 
  formatCurrency(columns = T, currency = "", digits = c(0, 0, 0, 2))

ggplot(tweets_hashtag$hash_freq, aes(hash_count, Freq)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Freq), vjust = 1.2, col = "white", size = 7)
```

## Top Hashtags

```{r top_hashtags}
datatable(tweets_hashtag$top_hashtags, rownames = F, width = "60%", filter = "top", 
          extensions = "Scroller", 
          options = list(dom = "ti", scroller = T, scrollY = 350))
```

## Mention Summary

```{r mention_summary}
datatable(tweets_mention$mention_summary, rownames = F, 
          options = list(dom = "t"), width = "60%") %>% 
  formatCurrency(columns = T, currency = "", digits = c(0, 0, 0, 2))

ggplot(tweets_mention$mention_freq, aes(mention_count, Freq)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Freq), vjust = 1.2, col = "white", size = 7)
```

## Top Mentions

```{r top_mentions}
datatable(tweets_mention$top_mentions, rownames = F, width = "60%", filter = "top",
          options = list(dom = "tilp")) %>%
  formatCurrency(columns = T, currency = "", digits = 0)
```

* Does not include mentions in rewteets, only "proactive" mentions

## Keywords

```{r keywords_table}

datatable(as.data.frame(my_words), options = list(dom = ""), width = "35%")
```

## Word Summary

```{r word_summary}
datatable(tweets_word$word_summary, rownames = F, options = list(dom = "t"),
          width = "60%") %>% 
  formatCurrency(columns = T, currency = "", digits = c(0, 0, 0, 2))

ggplot(tweets_word$word_freq, aes(word_count, Freq)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = Freq), vjust = 1.2, col = "white", size = 7)


```

## Top Words

```{r top_words}
datatable(tweets_word$top_words, rownames = F, width = "60%", filter = "top",
          options = list(dom = "tilp")) %>% 
  formatCurrency(columns = T, currency = "", digits = 0)
```

